\documentclass[11pt, a4paper,sans]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[scale=0.85]{geometry}
\geometry{top=2cm,bottom=1.5cm} 
\setlength{\hintscolumnwidth}{3.3cm}
\firstname{Jiaqin}
\familyname{Wu}
\mobile{(86) 134-8224-8154}
\email{jiaqin.wu.zh@gmail.com}
%\quote{Target: Senior Software Developer, Field Application Engineer, \\Software Test Engineer.}

\begin{document}
\maketitle

\section{Summary}
\cvlistdoubleitem{Date of Birth: Dec. 27th, 1986}{Gender: Male}
\cventry{}{I have 7 years of experience in software development, 2 years of experience in a system architecture role. I can speak English(CET-6) and Japanese(JLPT 2).I'm a quick learner, and very glad to share my experience with other people}{}{}{}{}

\section{Experience}
\cventry{2014.4 -- today}{System Architecture}{PATAC Shanghai}{}{}{Infotaiment Group in PATAC Shanghai is responsible for the development of all the Local vehicle IVI system for Buick, Chevrolet and Cadillac.
\begin{itemize}%
\item Research and design the software system for next generation infotainment based on hypervisor.
\item Evaluate Android system ability, give solution to customize Android framework to meet infotainment specifications, such as Audio/Video, CAN Service, T-Box. etc.
\item Develop concept software to evaluate software design.
\item Write all the function specifications. Design prototypes of UI and flowchart.
\item Write data structure and interface for software modules.
\item Manage project development according to agile principle, help developers to investigate and fix bugs, in order to ensure software will be deliver on time. (These projects has been deployed on many Bucik and Chevrolet vehicle such as Excelle XT. etc.)
\end{itemize}}

\cventry{2010.12 -- 2014.4}{Software Developer}{DragonWave Inc. Shanghai}{}{}{DragonWave provide microwave mobile back-hall solutions.
\begin{itemize}%
\item Maintain and debug Operating System, such as VxWorks, Linux, QNX.
\item Transplant OS wrapper from VxWorks to Linux to keep interface compatibility.
\item Add and modify Net-Snmp in Linux system to support Simple Network Manage Protocal(SNMP).
\item Transplant and maintain Management Information Base(MIB), support add, delete, search, support backup and restore, support TRAP.
\item Boot up new project, and maintain projects Makefile.
\item Add vstfp, openssh, lighttpd for Linux system.
\item Log CPU Usage, Memory Usage, Throughput, generate XML file. Optimize TinyXML write performance.
\item Modify Linux user password authentic.
\end{itemize}}

\cventry{2009.4 -- 2010.9}{Software Engineer}{BravoTech Inc. Shanghai Digital R\&D Center}{}{}{BravoTech develop Low-Cost Fiber Optic Repeater.
\begin{itemize}%
\item Test and Debug Xilinx MicroBlaze Soft Core MCU, Flash Memory, Serial Port, SPI Bus.
\item Debug Clock, D/A, A/D chips.
\item Write Verilog HDL code to implement DDC/DUC SPI control memory interface.
\item Test SERDES and MDIO interface.
\end{itemize}}

\section{Training \& Education}
\cventry{2008.7 -- 2009.3}{Trainee}{Fullcast Technology Co., Ltd}{}{}{{}
\begin{itemize}%
\item Embedded Software Development.
\begin{itemize}
\item ARM Architecture.
\item Linux OS.
\item Driver.
\item Cross Compile.
\end{itemize}
\end{itemize}}

\cventry{2004.9 -- 2008.6}{Student}{Telecommunication Major, Information and Technology Institute, DongHua University}{}{}{{}
\begin{itemize}
\item 2nd Prize of 2007 Sony Cup National Undergraduate Electronic Designing Contest, Shanghai.
\end{itemize}}

\section{Skills \& Expertise}
\cvline{Familiar Languages}{C programming language, C++.}
\cvline{Knowing Languages}{VBA, ML, Python.}
\cvline{Learning Languages}{C Sharp, .Net Framework}
\cvline{Knowing OS}{Linux, QNX, VxWorks, Nucleus}
\cvline{Familiar Tools}{Visual Studio, Doxygen, Vim, Microsoft Project, Office.}
\cvline{Others}{Database principle and implementation.}

\end{document}
